Automated Topic Naming

### 2012-01-17 ese/ese.tex
4. Reviewer 3 raises that the extremely low IRR (~0.1) threatens the    validity of the results of these experiments, and its threats to    validity should be made more prominent.    - [X] Threats to validity updated for low IRR    - [X] Suggestions on improvement

After some discussion we concluded that usability was a source of
disagreement. Do user manuals improve usability? Is a command-line
option a usability issue? These kinds of questions illustrate some of
the agreement, disagreement and ambiguity about these labels. Furthermore, 
both annotators found that the annotation was time-consuming and
difficult.

@@

We assessed inter-rater reliability (IRR), a measure of the correlation between the manual annotations the first two authors created. Perfect IRR (1.0) indicates complete agreement 
on the appropriate annotation for that topic. We verified IRR using
manually annotated PostgreSQL topics, and achieved a weak result of $0.1$.
Some of the reasons for this are a disagreement over the appropriate classification for documentation topics (should this be considered
usability or portability?). A short education session on what a given NFR from the ISO standard encompasses would reduce this error rate.

@@

We validated our topic labelling techniques using multiple experiments. % on unsupervised learners, supervised and multi-label learners. 
We first conducted semi-unsupervised labelling using word-lists. 
Our next approach was supervised, using single-label and multi-label learners. 
Both kinds of learners performed well with average
%area under the 
ROC values between $0.6$ and $0.8$. These results, along with the efficient performance of our learners, demonstrate that labelled topic extraction is
a promising approach for understanding the occurrence of non-functional requirements in software projects. 
%Although it may seem like common knowledge that maintenance is a concern as a project matures, our technique was able to show this independently.
%We showed that NFRs are often trending topics in commit comments
%, and that NFRs are quite common as developer topics.
%; and that there are efficient methods of automating topic labelling.

>>>>

After some discussion we concluded that usability was a source of
disagreement. Do user manuals improve usability? Is a command-line
option a usability issue? These kinds of questions illustrate some of
the agreement, disagreement and ambiguity about these labels. 
Thus we would recommend that future annotators make a concerted effort
to train and discuss when one applies an annotation.
Furthermore, 
both annotators found that the annotation was time-consuming and
difficult.

We feel that this resulting IRR score, although lackluster, indicates
the underlying difficulty of annotating such a data-set.
Consistent training of the annotators (the people) might avoid low IRR scores, or
using more annotators.
Other improvements could be gained by approaching some of the original developers
and using their expertise to annotate the data according to their intent.
Thus improvements
could be gained by producing more robust training samples that use
multiple raters, or experts, who are similarly trained and willing to discuss and
negotiate disagreements.

@@

We assessed inter-rater reliability (IRR), a measure of the correlation between the manual annotations the first two authors created. Perfect IRR (1.0) indicates complete agreement 
on the appropriate annotation for that topic. We verified IRR using
manually annotated PostgreSQL topics, and achieved a weak result of $0.1$.
Some of the reasons for this are a disagreement over the appropriate classification for documentation topics (should this be considered
usability or portability?). A short education session on what a given
NFR from the ISO standard encompasses would reduce this error rate.
Weak IRR results could also be responsible for some the low ROC
performance, if each rater is picking up on different information it
might make it more difficult to train a machine learner to do the
same.
Furthermore weak IRR results threatens the validity of the
experiments, if raters cannot agree then consistently labelling by
ISO-9126 related NFRs could be quite difficult.

@@

We validated our topic labelling techniques using multiple experiments. % on unsupervised learners, supervised and multi-label learners. 
We first conducted semi-unsupervised labelling using word-lists. 
Our next approach was supervised, using single-label and multi-label learners. 
Both kinds of learners performed well with average
%area under the 
ROC values between $0.6$ and $0.8$. 
These results were confounded by our low inter-rater reliability score
on the PostgreSQL data-set, suggesting that annotators need careful
and thoughtful training.
With appropriate rigor in annotation, these results, along with the performance of our learners,
demonstrate that labelled topic extraction can be
a promising approach for understanding the occurrence of non-functional requirements in software projects. 
%Although it may seem like common knowledge that maintenance is a concern as a project matures, our technique was able to show this independently.
%We showed that NFRs are often trending topics in commit comments
%, and that NFRs are quite common as developer topics.
%; and that there are efficient methods of automating topic labelling.
